Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-03 WSSSPE2_report/WSSSPE2_review.tex
Section 4: Mini-summaries.

@@

@@

\item Alice Allen: Find it! Cite it!
\end{enumerate}

>>>>

James sought to provoke discussion by proposing that papers whose workflows are
not kept current with the changing software ecosystem should be automatically
retracted. This would create the right incentive for authors to keep their
software current and usable, rather than the current situation in which every
potential user has to do this individually. A softer version of the proposal
would identify papers whose software workflow has become bit-rotten and allow
others to keep the code up to date, either adding them as new authors of the
paper or providing credit in some other form for their academic service.

@@

I described how the rOpenSci project has been successful by focusing not just on
building software but on building a community of researchers who learn and adopt
our approaches to reproducible research and sustainable software practice.
Through outreach, mentoring, workshops and hackathons, we have not only reached
new users, but turned users into co-developers of software and practices to
support data science research across a growing set of disciplines.

@@

\item Alice Allen: Find it! Cite it!

The Astrophysics Source Code Library (ASCL) is an online registry of
scientist-written software used in astronomy research. Our primary interest is
making research more transparent by making this software more discoverable for
examination. The ASCL is treated like a publication by the indexing resource for
astronomy, the Astrophysics Data System (ADS). ADS tracks citations to what it
indexes, including citations to ASCL entries. Increasing rewards for writing
software, whether through citation, transitive credit or other methods, gives
software authors a powerful reason to take the time to build sustainability into
their software and is an excellent way to drive community change. The ASCL
actively looks for opportunities to use change management strategies to move
astronomy to a more transparent discipline; these strategies can be used in
other disciplines to further change in them. 
\end{enumerate}
